Job Demands-Resources model components through the lens of O*NET classifications

### 2022-03-23 Submission.tex
Study 1 charts

Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al. (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net. A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.

@@

The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A. B. Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).

Thus, a fourth question of interest explores just that possibility:

@@

>>>>

Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al. (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net. We aim to present evidence surrounding whether O*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.

@@

While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification. There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A. B. Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)). Thus, Study 2 focuses on a fourth question of interest.

@@

\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.
